Additional analysis

### 2018-07-15 03_additional-analysis.Rmd
Stop using file.path(here())

source(file.path(here(), "lib", "graphics.R"))
source(file.path(here(), "lib", "pander_options.R"))
source(file.path(here(), "lib", "modeling.R"))

# Load data
results <- readRDS(file.path(here(), "data", "results_clean.rds"))
```

@@

```{r build-consort}
consort <- readRDS(file.path(here(), "data", "completion_summary.rds")) %>% 
  spread(reason, n) %>% 
  mutate(group = 1:n(),
         assigned = Approved + `Failed first attention check`,
         issue = str_replace_all(issue, "assistance", "assist.")) %>% 
  mutate(assigned_label = glue("Allocated to Group {group}\n{crackdown}\n{issue}\n{funding} funding\n\nN = {assigned}"),
         completed_label = glue("Completed\nN = {Approved}\n\n{`Failed first attention check`} failed\nattention check"))

@@

# Save as PDF
cairo_pdf(filename = file.path(here(), "output", "figures", "consort.pdf"),
          width = 10, height = 6)
grid.newpage()
walk(full_chart, ~ print(.))
invisible(dev.off())

# Save as PNG
png(filename = file.path(here(), "output", "figures", "consort.png"), 
    width = 10, height = 6, units = "in",
    bg = "white", res = 300, type = "cairo")
grid.newpage()
walk(full_chart, ~ print(.))
invisible(dev.off())

@@

```{r load-clean-cps, warning=FALSE, message=FALSE}
cps_2015_ddi_file <- file.path(here(), "data", "ipums-cps", "cps_09_2015.xml")
cps_2015_data_file <- file.path(here(), "data", "ipums-cps", "cps_09_2015.dat.gz")

@@

cps_2017_ddi_file <- file.path(here(), "data", "ipums-cps", "cps_2017.xml")
cps_2017_data_file <- file.path(here(), "data", "ipums-cps", "cps_2017.dat.gz")

@@

```{r compile-stan-model, warning=FALSE, message=FALSE, cache=TRUE}
prop_test_bayes_saved <- file.path(here(), "lib", "bayes_prop_test.rds")

if (file.exists(prop_test_bayes_saved)) {
  prop_test_bayes <- readRDS(prop_test_bayes_saved)
} else {
  prop_test_bayes <- stan_model(file.path(here(), "lib", "bayes_prop_test.stan"))
  saveRDS(prop_test_bayes, prop_test_bayes_saved)
}
```

@@

tbl_sample_pop %>% 
  pandoc.table.return(keep.line.breaks = TRUE, style = "multiline", justify = "lcccc", 
                      caption = "Characteristics of experimental sample {#tbl:exp-sample}") %T>% 
  cat(file = file.path(here(), "output", "tables", "tbl-exp-sample.md")) %>% 
  cat()
```

@@

plot_avg_time %T>% 
  print() %T>%
  ggsave(., filename = file.path(here(), "output", "figures", "avg-time.pdf"),
         width = 4, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "avg-time.png"),
         width = 4, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r tbl-models-amount-full, warning=FALSE, results="asis"}
huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-models-amount-full.md"))
```

@@

```{r tbl-models-likely-full, warning=FALSE, results="asis"}
huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-models-likelihood-full.md"))
```

>>>>

source(here("lib", "graphics.R"))
source(here("lib", "pander_options.R"))
source(here("lib", "modeling.R"))

# Load data
results <- readRDS(here("data", "results_clean.rds"))
```

@@

```{r build-consort}
consort <- readRDS(here("data", "completion_summary.rds")) %>% 
  spread(reason, n) %>% 
  mutate(group = 1:n(),
         assigned = Approved + `Failed first attention check`,
         issue = str_replace_all(issue, "assistance", "assist.")) %>% 
  mutate(assigned_label = glue("Allocated to Group {group}\n{crackdown}\n{issue}\n{funding} funding\n\nN = {assigned}"),
         completed_label = glue("Completed\nN = {Approved}\n\n{`Failed first attention check`} failed\nattention check"))

@@

# Save as PDF
cairo_pdf(filename = here("output", "figures", "consort.pdf"),
          width = 10, height = 6)
grid.newpage()
walk(full_chart, ~ print(.))
invisible(dev.off())

# Save as PNG
png(filename = here("output", "figures", "consort.png"), 
    width = 10, height = 6, units = "in",
    bg = "white", res = 300, type = "cairo")
grid.newpage()
walk(full_chart, ~ print(.))
invisible(dev.off())

@@

```{r load-clean-cps, warning=FALSE, message=FALSE}
cps_2015_ddi_file <- here("data", "ipums-cps", "cps_09_2015.xml")
cps_2015_data_file <- here("data", "ipums-cps", "cps_09_2015.dat.gz")

@@

cps_2017_ddi_file <- here("data", "ipums-cps", "cps_2017.xml")
cps_2017_data_file <- here("data", "ipums-cps", "cps_2017.dat.gz")

@@

```{r compile-stan-model, warning=FALSE, message=FALSE, cache=TRUE}
prop_test_bayes_saved <- here("lib", "bayes_prop_test.rds")

if (file.exists(prop_test_bayes_saved)) {
  prop_test_bayes <- readRDS(prop_test_bayes_saved)
} else {
  prop_test_bayes <- stan_model(here("lib", "bayes_prop_test.stan"))
  saveRDS(prop_test_bayes, prop_test_bayes_saved)
}
```

@@

tbl_sample_pop %>% 
  pandoc.table.return(keep.line.breaks = TRUE, style = "multiline", justify = "lcccc", 
                      caption = "Characteristics of experimental sample {#tbl:exp-sample}") %T>% 
  cat(file = here("output", "tables", "tbl-exp-sample.md")) %>% 
  cat()
```

@@

plot_avg_time %T>% 
  print() %T>%
  ggsave(., filename = here("output", "figures", "avg-time.pdf"),
         width = 4, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "avg-time.png"),
         width = 4, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r tbl-models-amount-full, warning=FALSE, results="asis"}
huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = here("output", "tables", "tbl-models-amount-full.md"))
```

@@

```{r tbl-models-likely-full, warning=FALSE, results="asis"}
huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = here("output", "tables", "tbl-models-likelihood-full.md"))
```
